`gosset`: An R package for analysis and synthesis of ranking data in agricultural

### 2022-06-24 inst/paper/paper.Rmd
Update paper.Rmd

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural
  experimentation'
abstract: null
output:
  pdf_document:
    fig_caption: yes
    number_sections: no
    keep_tex: no
  word_document: default
latex_engine: pdflatex
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
csl: apa.csl
header-includes:
- \usepackage{pdfpages}
- \usepackage{caption}
- \usepackage{xcolor}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{font=small}
---

@@

* `plot` provides an alternative method to the default plot function of the PlackettLuce package.  
* `regret` computes the regret [@Loomes_1982;  ].  
* `reliability` computes the reliability of crop varieties, the probability to outperform the reference variety [@eskridge_1992].  
* `worth_bar`  creates a bar plot of the estimated worth values for each evaluated variety.  
* `worth_map` creates a heatmap plot of the estimated worth values for all varieties considering each of the
evaluated traits.

@@

data("nicabean", package = "gosset")

@@

```{r , message=FALSE, eval=FALSE, echo=TRUE}
R <- vector(mode = "list", length = length(traits))

@@

```{r , message=FALSE, eval=FALSE, echo=TRUE}

@@

>>>>

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural
  experimentation'
abstract: null
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    number_sections: no
    keep_tex: no
latex_engine: pdflatex
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
csl: apa.csl
header-includes:
- \usepackage{pdfpages}
- \usepackage{caption}
- \usepackage{xcolor}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{font=small}
---

@@

* `plot` provides an alternative method to the default plot function of the PlackettLuce package.  
* `regret` computes the regret [@Loomes_1982].  
* `reliability` computes the reliability of crop varieties, the probability to outperform the reference variety [@eskridge_1992].  
* `worth_bar`  creates a bar plot of the estimated worth values for each evaluated variety.  
* `worth_map` creates a heatmap plot of the estimated worth values for all varieties considering each of the
evaluated traits.

@@

data("nicabean", package = "gosset")
load("nicabean_temp_ind.rda")

@@

```{r , message=FALSE, eval=TRUE, echo=TRUE}
R <- vector(mode = "list", length = length(traits))

@@

```{r , message=FALSE, eval=TRUE, echo=TRUE}

@@

Table 3 shows the results of reliability for the evaluated common bean varieties in each of 
the resulting nodes of the Plackett-Luce tree.

```{r rel1, message=FALSE, eval=TRUE, echo=FALSE}
nicabean_rel <- reliability(pl, ref = "Amadeus 77")

kable(t(nicabean_rel), col.names = c("node 2", "node 3"), caption = "Reliability of evaluated varieties
      in each of the resulting nodes of the Plackett-Luce tree")
